Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-11 report/report.tex
Update collision study, implementation

The maximum distance between two features was set to 1 times the positional accuracy, since then there will always be ample room to make changes to any features that would collide with the newly moved nodes, and thus collisions propagating will not be an issue.
In this implementation, roads of different types were allowed to merge into one another to form common intersections.
To facilitate this, it was neccessary to work with a path-by-path representation of the point data.
When two path share a node with common coordinates, they form an intersection which can be of multiple different types.

See the footnote for the publication that the default minimum widths were obtained from. \footnote{Vägars och gators utformning - Trafikverket. Publikation 2020:029. https://trafikverket.ineko.se/Files/sv-SE/71830/\\Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf}
The standard recommended minimum width for a two-lane road in Sweden is 6.5 meters.

Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
Table \ref{table:road-widths} shows the minimum and maximum road widths that were found during these measurements, and that will be used in the collision study.

@@

Here a few special cases are noted:
\begin{enumerate}
    \item If two roads intersect even though they share a node, it is a natural connection in the road network and should not be counted as a problematic case of feature overlap.
    \item Collisions between tunnels or bridges and other roads were ignored since these are of different heights. Brdiges and tunnels were identified by looking at feature attributes in OSM.
    \item Any roads that were represented as polygons or multipolygons instead of ploylines were also excluded from the study. These are typically town squares or areas designated for walking.
\end{enumerate}

>>>>

The standard road widths were obtained from a publication by the Swedish Transport Administration
\footnote{Vägars och gators utformning - Trafikverket. Publikation 2020:029. https://trafikverket.ineko.se/Files/sv-SE/71830/\\Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf}
, and were presented as requirements on the minimum lane width for certain types of roads and applications.
These regulated minimum widths were used as a lower bound road with when examining the OSM dataset for potential collisions.
The upper bound was found by visual measurements of a few key locations in the Stockholm area using the Bing maps service.
Table \ref{table:road-widths} shows the minimum and maximum road widths that will be used in the collision study.

@@

Finally, a few special cases where features or feature collisions should not be registered were neccessary to implement:
\begin{enumerate}
    \item If two roads intersect even though they share a node, it is a natural connection in the road network and should not be counted as a problematic case of feature overlap.
    \item Collisions between tunnels or bridges and other roads were ignored since these are of different heights. Brdiges and tunnels were identified by looking at feature attributes in OSM.
    \item Any roads that were represented as polygons or multipolygons instead of ploylines were also excluded from the study. These are typically town squares or areas designated for walking.
\end{enumerate}
